Flexibility of interactions depends on habitat suitability

### 2019-09-13 paper/manuscript.Rmd
Fix size of double column figure

```{r fig-random-effects, fig.width = width('double'), fig.height = 2.2*2, fig.cap = fig_random_effects_legend}
loadd(random_species_draws)

>>>>

```{r fig-random-effects, fig.width = width('double'), fig.height = 2.2*2, fig.cap = fig_random_effects_legend, out.width = "6.81in", out.height = "4.4in", out.extra="center"}
loadd(random_species_draws)
